---
title: "Replicate the tidymodel workflow"
output: html_notebook
---

# Preparation

```{r}
setwd("C:/Users/wenyu/Documents/algorithm/R/taste_tidymodel")
library(tidyverse,)
library(tidymodels)
```
# Pre-Process

## Data Sampling
```{r}
iris_split <- initial_split(iris, prop = 0.6)
iris_split
```

## a glimpse of the data
```{r}
iris_split %>%
  training() %>%
  glimpse()
```

## Pre-process interface

In tidymodels, the recipes package provides an interface that specializes in data pre-processing. Within the package, the functions that start, or execute, the data transformations are named after cooking actions.
```{r}
iris_recipe <- training(iris_split) %>%
  recipe(Species ~.) %>%
  step_corr(all_predictors()) %>%
  step_center(all_predictors(), -all_outcomes()) %>%
  step_scale(all_predictors(), -all_outcomes()) %>%
  prep()

iris_recipe 


# Execute the pre-processing
# The testing data can now be transformed in the exact same way with one function bake()

iris_testing <- iris_recipe %>%
  bake(testing(iris_split)) 
# Performing the same operation over the training data is redundant, because that data has already been prepped. To load the prepared training data into a variable, we use juice(). It will extract the data from the iris_recipe object.
iris_training <- juice(iris_recipe)
```


# Model Training
Instead of replacing the modeling package, tidymodels replaces the interface. Better said, tidymodels provides a single set of functions and arguments to define a model. It then fits the model against the requested modeling package.

In the example below, the rand_forest() function is used to initialize a Random Forest model. To define the number of trees, the trees argument is used. To use the ranger version of Random Forest, the set_engine() function is used. Finally, to execute the model, the fit() function is used. The expected arguments are the formula and data. Notice that the model runs on top of the juiced trained data.

```{r}
iris_ranger <- rand_forest(trees = 100, mode = "classification") %>%
  set_engine("ranger") %>%
  fit(Species ~ ., data = iris_training)

iris_rf <-  rand_forest(trees = 100, mode = "classification") %>%
  set_engine("randomForest") %>%
  fit(Species ~ ., data = iris_training)

iris_svmrbf <- svm_rbf(mode="classification") %>% 
    set_engine("kernlab") %>%
    fit(Species ~ ., data = iris_training)
```

# Preditions

```{r}
iris_ranger
iris_ranger %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing) %>%
  glimpse()
iris_svmrbf


```

# Model Validation


with metrics() function, which will automatically choose metrics appropriate for a given type of model.
```{r}
iris_rf %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing) %>%
  metrics(truth = Species, estimate = .pred_class)

iris_rf %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing) %>%
  metrics(truth = Species, estimate = .pred_class)


```

## Per classifier metrics
It is easy to obtain the probability for each possible predicted value by setting the type argument to prob. 
That will return a tibble with as many variables as there are possible predicted values. Their name will default to the original value name, prefixed with .pred_.


```{r}
iris_ranger %>%
  predict(iris_testing, type = "prob") %>%
  glimpse()

iris_probs <- iris_ranger %>%
  predict(iris_testing, type = "prob") %>%
  bind_cols(iris_testing)
glimpse(iris_probs)

```

Now that everything is in one tibble, it is easy to calculate curve methods.
In this case we are using gain_curve()??
```{r}
iris_probs%>%
  gain_curve(Species, .pred_setosa:.pred_virginica) %>%
  glimpse()

# The curve methods include an autoplot() function that easily creates a ggplot2 visualization. 

iris_probs%>%
  gain_curve(Species, .pred_setosa:.pred_virginica) %>%
  autoplot()
```



```{r}
iris_probs%>%
  roc_curve(Species, .pred_setosa:.pred_virginica) %>%
  autoplot()
```

## additional accuracy matrix
I also need to know how the metrics function is working??
```{r}

iris_ranger %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing) %>%
  metrics(truth = Species, estimate = .pred_class)

iris_ranger %>% 
  predict(iris_testing, type = "prob") %>%
  bind_cols(predict(iris_ranger, iris_testing)) %>%
  bind_cols(select(iris_testing, Species)) %>%
  glimpse()

iris_ranger %>% 
  predict(iris_testing, type = "prob") %>%
  bind_cols(predict(iris_ranger, iris_testing)) %>%
  bind_cols(select(iris_testing, Species)) %>%
  metrics(Species, .pred_setosa:.pred_virginica, estimate = .pred_class)
```

